Musical Ornaments

### 2018-05-11 slides/pnwplse.tex
more work on talk

\begin{frame}\frametitle{Music Representation}
\ExecuteMetaData[../agda/latex/Pnwplse.tex]{pitch}
\ExecuteMetaData[../agda/latex/Pnwplse.tex]{duration}
\ExecuteMetaData[../agda/latex/Pnwplse.tex]{note}
\ExecuteMetaData[../agda/latex/Pnwplse.tex]{music}
\end{frame}

>>>>

\begin{frame}\frametitle{What will programming look like in 50 years?}
\begin{itemize}
\item Convergence of math and computer science
\item Functional Programming, Algebra of Programming
\item Dependent Types or a successor (Cubical?)
\item Who does the programming?
\end{itemize}
\end{frame}

\begin{frame}\frametitle{How do we get there from here?}
\begin{itemize}
\item Add dependent types to an industrial-strength language (Haskell)
\item Make a dependently typed language (Agda, Idris) practical to use
\item Learn how to program using dependent types
\item Many theoretical and practical advances are still needed
\end{itemize}
\end{frame}

\begin{frame}\frametitle{Euterpea}
\begin{figure}
\includegraphics[height=0.8\textheight]{hsom}
\end{figure}
\end{frame}

\begin{frame}\frametitle{Look vs Time (1997)}
\begin{figure}
\includegraphics[width=\textwidth]{lookVsTime}
\end{figure}
\end{frame}

\begin{frame}\frametitle{Music Representation \`a la Euterpea}
\ExecuteMetaData[../agda/latex/Pnwplse.tex]{pitch}
\ExecuteMetaData[../agda/latex/Pnwplse.tex]{duration}
\ExecuteMetaData[../agda/latex/Pnwplse.tex]{note}
\ExecuteMetaData[../agda/latex/Pnwplse.tex]{music}
\end{frame}
